---
title: "Week 2 exercises "
date: 2025-05-06
output: html_document
---
```{r }
library(tidyverse)
library(lubridate)

magnets <- read.csv('magnets.csv')
str(magnets)
summary(magnets)
```

Day 3 


#  Question 9.1. 

#  1. What is the sample average of the change in score between the patients
#  rating before the application of the device and the rating after the application?
```{r }
head(magnets)

mean(magnets$change)
```

#  2. Is the variable active a factor or a numeric variable?
#  11Vallbona, Carlos, Carlton F. Hazlewood, and Gabor Jurida. (1997). Response of pain to
#  static magnetic elds in postpolio patients: A double-blind pilot study. Archives of Physical
#  and Rehabilitation Medicine 78(11): 1200-1203.

it is a factor

# 9.5. SOLVED EXERCISES
#  153
#  3. Compute the average value of the variable change for the patients that
#  received and active magnet and average value for those that received an
#  inactive placebo. (Hint: Notice that the rst 29 patients received an active
#  magnet and the last 21 patients received an inactive placebo. The sub
# sequence of the rst 29 values of the given variables can be obtained via
#  the expression change[1:29] and the last 21 vales are obtained via the
#  expression change[30:50] .)



#  4. Compute the sample standard deviation of the variable change for the
#  patients that received and active magnet and the sample standard devia
# tion for those that received an inactive placebo.
#  5. Produce a boxplot of the variable change for the patients that received
#  and active magnet and for patients that received an inactive placebo.
#  What is the number of outliers in each subsequence?




# Question 10.1.
 In Subsection 10.3.2 we compare the average against the mid
range as estimators of the expectation of the measurement. The goal of this
 exercise is to repeat the analysis, but this time compare the average to the
 median as estimators of the expectation in symmetric distributions.
 1. Simulate the sampling distribution of average and the median of a sample
 of size n = 100 from the Normal(32) distribution. Compute the expec
tation and the variance of the sample average and of the sample median.
 Which of the two estimators has a smaller mean square error?
 2. Simulate the sampling distribution of average and the median of a sample
 of size n = 100 from the Uniform(0555) distribution. Compute the
 expectation and the variance of the sample average and of the sample
 median. Which of the two estimators has a smaller mean square error?






# Question 10.2. 
The goal in this exercise is to assess estimation of a proportion
 in a population on the basis of the proportion in the sample.
 The le pop2.csv was introduced in Exercise 7.1 of Chapter 7. This le
 contains information associated to the blood pressure of an imaginary popu
lation of size 100,000. The le can be found on the internet (http://pluto.
 huji.ac.il/~msby/StatThink/Datasets/pop2.csv). One of the variables in
 the le is a factor by the name group that identi es levels of blood pressure.
 The levels of this variable are HIGH , LOW , and NORMAL .
 The le ex2.csv contains a sample of size n = 150 taken from the given
 population. This le can also be found on the internet (http://pluto.huji.
 ac.il/~msby/StatThink/Datasets/ex2.csv). It contains the same variables
 as in the le pop2.csv . The le ex2.csv corresponds in this exercise to
 the observed sample and the le pop2.csv corresponds to the unobserved
 population.
 Download both les to your computer and answer the following questions:
 1. Compute the proportion in the sample of those with a high level of blood
 pressure16.
 2. Compute the proportion in the population of those with a high level of
 blood pressure
 3. Simulate the sampling distribution of the sample proportion and compute
 its expectation.
 4. Compute the variance of the sample proportion.
 5. It is proposed in Section 10.5 that the variance of the sample proportion
 is Var( P) = p(1 p) n, where p is the probability of the event (having a
 high blood pressure in our case) and n is the sample size (n = 150 in our
 case). Examine this proposal in the current setting.


 ```{r exercise10.2}
ex2 <- read.csv(ex2.csv)










## Day 4

# Questions 12.1. 

Consider a medical condition that does not have a standard 
treatment. The recommended design of a clinical trial for a new treatment
 to such condition involves using a placebo treatment as a control. A placebo
 treatment is a treatment that externally looks identical to the actual treatment
 but, in reality, it does not have the active ingredients. The reason for using
 placebo for control is the placebo effect . Patients tent to react to the fact that
 they are being treated regardless of the actual bene cial e ect of the treatment.
 As an example, consider the trial for testing magnets as a treatment for pain
 that was described in Question 9.1. The patients that where randomly assigned
 to the control (the last 21 observations in the le magnets.csv ) were treated
 with devises that looked like magnets but actually were not. The goal in this
 exercise is to test for the presence of a placebo e ect in the case study Magnets
 and Pain Relief of Question 9.1 using the data in the le magnets.csv .
 
 
 1. Let X be the measurement of change, the difference between the score of
 pain before the treatment and the score after the treatment, for patients
 that were treated with the inactive placebo. Express, in terms of the
 expected value of X, the null hypothesis and the alternative hypothesis
 for a statistical test to determine the presence of a placebo e ect. The null
 hypothesis should re ect the situation that the placebo e ect is absent.


 2. Identify the observations that can be used in order to test the hypotheses.


 3. Carry out the test and report your conclusion. (Use a signi cance level of
 5%.)









 ```{r day4  }

magnets <- read.csv('magnets.csv')
str(magnets)
summary(magnets)






 ```